Make any stupid plot you want

### 2021-03-01 draft/sections/math.tex
q hat

\subsubsection{Visual Encoders \vchannel}
\label{sec:artist_nu}
%% equivariant maps 
\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/equivariance_nu.png}
    \caption{In this artis, \vchannel\ maps the strings to the emojis. This \vchannel\ is equivariant because the monoid actions (which are represented by the colored arrows) are the same on both the \dsection\ input and \vsection\ output sets.}
    \label{fig:artist_nu}
\end{figure}
As introduced in section~\ref{sec:intro_viz}, there are many ways to visually represent data components. We define the visual transformers \vchannel\ 
\begin{equation}
    \label{eq:nu_expanded}
    \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
\end{equation}
as the set of equivariant maps $\vchannel_i: \dsection_i \mapsto \vsection_i$. Given $\monoid_i$ is the monoid action on $\dtotal_i$ and that there is a monoid ${\monoid_i}^{\prime}$ on $\vtotal_i$, then there is a monoid homomorphism from $\monoid_i \rightarrow {\monoid_i}^{\prime}$ that \vchannel\ must preserve. As mentioned in section~\ref{sec:data_monoid}, we choose monoid actions as the basis for equivariance because they define the structure on the fiber components.

@@

\subsubsection{Graphic Assembler \vmark}
\label{sec:artist_q}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \caption{\vchannel\ functions convert data $\dsection_i$ to visual characteristics $\vsection_i$, then \vmark\ assembles $\vsection_i$ into a graphic $\gsection$ such that there is a map \vindex\ preserving the continuity of the data. \gsection\ applied to a region of connected components $\gbase_{\dbasepathpoint}$  generates a part of a graphic, for example the point graphical mark.} 
    \label{fig:artist_q}
\end{figure}

@@

Lets call the visual representations of the components $\Gamma(\vtotal)=X$ and the graphic $\vmark(\Gamma(\vtotal))=Y$. If for all monoids $m \in \monoid$ and for all $\vsection, \vsection^{\prime} \in X$, the output is equivalent 
\begin{equation}
\vmark(\vsection) = \vmark(\vsection^{\prime})\implies \vmark(m\circ\vsection) = \vmark(m\circ\vsection^{\prime})
\end{equation}
then a group action on $Y$ can be defined as $m\circ \gsection = \gsection^{\prime}$. The transformed graphic $\gsection^{\prime}$ is equivariant to a transform on the visual bundle $\gsection^{\prime}=\vmark(m\circ \vsection)$ on a section that $\vsection \in \vmark^{-1}(\gsection)$ that must be part of generating \gsection.

\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/diff_type_q.png}
    \caption{These two glyphs are generated by the same \vmark\ function, but differ in the value of the edge thickness parameter $\vsection_i$. A valid \vmark\ is one where a shift in $\vsection_i$ is reflected in the glyph generated by \gsection.}
    \label{fig:artist_mark_change}
\end{figure}

The glyph in figure~\ref{fig:artist_mark_change} has the following characteristics \vfiber\ specified by  $(xpos,\, ypos,\, color,\, thickness)$ such that one section is $\vsection=(0,0,0,1)$ and $\vmark(\vsection) = \gsection$ generates a piece of the thin hollow circle. The equivariance constraint on \vmark\ is that the action $m=(e, e, e, x+2)$, where e is identity, translates \vsection\ to  $\vsection^{\prime}=(e,e,e,3)$. The corresponding action on \gsection causes $\vmark(\vsection^{\prime})$ to be the thicker circle in figure~\ref{fig:artist_mark_change}.

@@

\subsubsection{Assembly factory \vmarkd}
The graphic base space \gbase\ is not accessible in many architectures, including Matplotlib; instead we can construct a factory function \vmarkd\ over \dbase\ that can build a \vmark. As shown in eq~\ref{eq:artist_diagram}, \vmark\ is a bundle map $\vmark: \vtotalpull\rightarrow \gtotal$ where \vtotalpull\ and \gtotal\ are both bundles over \gbase.
\begin{figure}[H]
    \includegraphics[width=.75\textwidth]{figures/math/q_hat.png}
    \caption{The pullback of the visual bundle \vtotalpull\ is the replication of a \vsection\ over all points \gbasepoint\ that map back to a single \dbasepoint. Because the \vsection\ is the same, we can constract a \vmarkd\ on \vsection\ over \dbasepoint\ that will fabricate the \vmark\ for the equivalent set of \gbasepoint\ associated to that \dbasepoint}
    \label{fig:artist_q_hat}
\end{figure}

>>>>

\subsubsection{Visual Encoders \vchannel}
\label{sec:artist_nu}
%% equivariant maps 
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/equivariance_nu.png}
    \caption{In this artis, \vchannel\ maps the strings to the emojis. This \vchannel\ is equivariant because the monoid actions (which are represented by the colored arrows) are the same on both the \dsection\ input and \vsection\ output sets.}
    \label{fig:artist_nu}
\end{figure}
As introduced in section~\ref{sec:intro_viz}, there are many ways to visually represent data components. We define the visual transformers \vchannel\ 
\begin{equation}
    \label{eq:nu_expanded}
    \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
\end{equation}
as the set of equivariant maps $\vchannel_i: \dsection_i \mapsto \vsection_i$. Given $\monoid_i$ is the monoid action on $\dtotal_i$ and that there is a monoid ${\monoid_i}^{\prime}$ on $\vtotal_i$, then there is a monoid homomorphism from $\monoid_i \rightarrow {\monoid_i}^{\prime}$ that \vchannel\ must preserve. As mentioned in section~\ref{sec:data_monoid}, we choose monoid actions as the basis for equivariance because they define the structure on the fiber components.

@@

\subsubsection{Graphic Assembler \vmark}
\label{sec:artist_q}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \caption{$\vchannel_i$ functions convert data $\dsection_i$ to visual characteristics $\vsection_i$, then \vmark\ assembles $\vsection_i$ into a graphic $\gsection$ such that there is a map \vindex\ preserving the continuity of the data. \gsection\ applied to a region of connected components $\gbase_{\dbasepathpoint}$  generates a part of a graphic, for example the point graphical mark.} 
    \label{fig:artist_q}
\end{figure}

@@

Lets call the visual representations of the components $\Gamma(\vtotal)=X$ and the graphic $\vmark(\Gamma(\vtotal))=Y$. If for all monoid actions $m \in \monoid$ and for all $\vsection, \vsection^{\prime} \in X$, the output is equivalent 
\begin{equation}
\vmark(\vsection) = \vmark(\vsection^{\prime})\implies \vmark(m\circ\vsection) = \vmark(m\circ\vsection^{\prime})
\end{equation}
then a monoid action on $Y$ can be defined as $m\circ \gsection = \gsection^{\prime}$. The transformed graphic $\gsection^{\prime}$ is equivariant to a transform on the visual bundle $\gsection^{\prime}=\vmark(m\circ \vsection)$ on a section that $\vsection \in \vmark^{-1}(\gsection)$ that must be part of generating \gsection.

\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/diff_type_q.png}
    \caption{These two glyphs are generated by the same \vmark\ function. The monoid 
    action $m_i$ on edge thickness $\vsection_i$ of the first glyph yields the thicker edge ${\vsection_i}^{\prime}$ in the second glyph.}
    \label{fig:artist_mark_change}
\end{figure}

The glyph in figure~\ref{fig:artist_mark_change} has the following characteristics \vfiber\ specified by  $(xpos,\, ypos,\, color,\, thickness)$ such that one section is $\vsection=(0,0,0,1)$ and $\vmark(\vsection) = \gsection$ generates a piece of the thin hollow circle. The equivariance constraint on \vmark\ is that the action $m=(e, e, e, x+2)$, where e is identity, translates \vsection\ to  $\vsection^{\prime}=(e,e,e,3)$. The corresponding action on \gsection\ causes $\vmark(\vsection^{\prime})$ to be the thicker circle in figure~\ref{fig:artist_mark_change}.

@@

\subsubsection{Assembly factory \vmarkd}
The graphic base space \gbase\ is not accessible in many architectures, including Matplotlib; instead we can construct a factory function \vmarkd\ over \dbase\ that can build a \vmark. As shown in eq~\ref{eq:artist_diagram}, \vmark\ is a bundle map $\vmark: \vtotalpull\rightarrow \gtotal$ where \vtotalpull\ and \gtotal\ are both bundles over \gbase.
\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/q_hat.png}
    \caption{The pullback of the visual bundle \vtotalpull\ is the replication of a \vsection\ over all points \gbasepoint\ that map back to a single \dbasepoint. Because the \vsection\ is the same, we can constract a \vmarkd\ on \vsection\ over \dbasepoint\ that will fabricate the \vmark\ for the equivalent set of \gbasepoint\ associated to that \dbasepoint}
    \label{fig:artist_q_hat}
\end{figure}
